\mytitle

### 2020-04-20 paper.tex
evaluation: finished experimental setting, moved to main results.

\paragraph{WFLO Instances and Energy Measurement}

To test and benchmark our models, we used 12 standard benchmark WFLO instances
from the literature~\cite{MOSETTI1994105,Zhang2014,grady2005placement}. 
The 12 benchmarks result from varying 2 wind settings (1 and 36 wind directions),
2 grid sizes ($10\times10$ with cell size $200$ meters and $20\times20$ with cell size $100$ meters),
and 3 variations for number of turbines ($m \in \{20, 30 or 40\}$).
The wind regime distribution presented in Figure~\ref{fig:prob_wind} was 
elicited from~\cite{Zhang2014}.
Additional parameters that were used to calculate 
the velocities ($u_{id\infty}, u_{ijd}$) include: turbine height ($60$ meters),
ground roughness ($0.3$ meters), turbine rotor radius ($20$ meters), and a wind farm of size $2km \times 2km$.
We have measured solutions using the SS energy expression.
To to this end, we converted solutions that came from LS based methods into the corresponding SS expression; 
the total mean energy is calculated in $kW/year$.

@@

For exact methods (QP-SS, ILP-LS, QP-lS and QUBO-LS),
we ran Gurobi with a time limit of 3600 seconds. We collected all feasible solutions
until that point in time. The best solution in terms of energy is the solution that attained the highest objective
values (SS in QP-SS and LS in the rest of the methods).
For the digital annealer, we used a single configuration that was found to work best across the different instances \todo{Jason, please insert details about the DA config. here} The DA ran until convergence of the underlying simulated annealing algorithm and the runtime 
of the procedure was recorded. \todo{@Chris: do we want to share the code that ran the experiments in batches? perhaps it should be separated from the problem construction and the two need to be shared separately}

@@

@@

\begin{table}[ht]

@@

\begin{table}[ht]

@@

\begin{figure}[t!]%

>>>>

\paragraph{Standard WFLO Instances}

To test and benchmark our models, we used 12 standard benchmark WFLO instances
from the literature~\cite{MOSETTI1994105,Zhang2014,grady2005placement}. 
The 12 benchmarks result from varying 2 wind settings (1 and 36 wind directions),
2 grid sizes ($10\times10$ with cell size $200$ meters and $20\times20$ with cell size $100$ meters),
and 3 variations for number of turbines ($m \in \{20, 30 or 40\}$). We denote by $\mathcal{W}$ the set of 12 instances. 
The wind regime distribution presented in Figure~\ref{fig:prob_wind} was 
elicited from~\cite{Zhang2014}.
Additional parameters that were used to calculate 
the velocities ($u_{id\infty}, u_{ijd}$) include: turbine height ($60$ meters),
ground roughness ($0.3$ meters), turbine rotor radius ($20$ meters), and a wind farm of size $2km \times 2km$.

@@

For exact methods (QP-SS, ILP-LS, QP-LS and QUBO-LS),
we ran Gurobi with a time limit of 3600 seconds. We collected all feasible solutions
until that point in time. The best solution in terms of energy is the solution that attained the highest objective
values (SS in QP-SS and LS in the rest of the methods).
For the digital annealer, we used a single configuration that was found to work best across the different instances \todo{Jason, please insert details about the DA config. here} The DA ran until convergence of the underlying simulated annealing algorithm and the runtime 
of the procedure was recorded. \todo{@Chris: do we want to share the code that ran the experiments in batches? perhaps it should be separated from the problem construction and the two need to be shared separately}

@@

\paragraph{Performance Measurement}

We have measured the total expected energy of a solution using the SS expression (see Eq.~(\ref{eq:ss}))\footnote{Note that the total mean energy is presented in $kW/year$.}.
The only method that optimizes on SS is QP-SS. Hence, for the other methods, we converted solutions
LS-based solution into the SS expression using Eq.~(\ref{eq:ss}) as proposed in~\cite{Zhang2014}. Specifically, let $x = (x_1, \ldots, x_k), k=n^2$ be a turbine placement solution obtained by an LS-based method.
Then, the SS based energy expression can be written as, 
$$\sum_{i\in \mathcal{N}}\sum_{d \in \mathcal{D}} \frac{1}{3} x_i \Bigg(u_{id,\infty} \Bigg[1-\sqrt{\sum_{j\in \mathcal{U}_{id}}x_j\bigg( 1-\frac{u_{ijd}}{u_{id,\infty}} \bigg) } \Bigg]    \Bigg)^3.$$

Next, we tested the performance of our approach as function of solution time. To this end, we 
compared the average performance of all LS-based methods on all 12 WFLO instances \footnote{The QP-SS method was not considered for performance over time, since it optimizes a different objective function.}. Since energy levels are not directly comparable between the different instances (due to varying number of turbines and wind farm specs) we used the \emph{mean relative error} (MRE) measure.

The MRE is defined with respect to the best solution obtained per instance and can be computed over time. Then, the
time-varying MRE can be averaged across the different scenarios and the average MRE (aMRE) can be used
for the desired comparison. We shall demonstrate the construction below.

Recall that $\mathcal{W}$ is the set of our 12 standard WFLO instances. 
Moreover, we let $b_w$ be the best energy solution (in terms of SS) obtained for an instance $w \in \mathcal{W}$ 
across the different LS-based methods. For example, the best solution (within 3600 seconds) for the second instance $w_2$ that aims at placing $30$ turbines on a $10\times10$ grid with a single wind regime is attained by QUBO-LS and the SS energy expression is $15742 kW/year$. Therefore, we let $b_w = 15742$. Then, for every point in time $t \in \{0,\ldots, 3600\}$ (measured in seconds), we can compute the relative error of a given approach per instance $w$. Let $\mathcal{A}$ be the set of solution approaches, $\mathcal{A}= \{QUBO-LS, QP-LS, DA-LS, ILP-LS\}$. Further, denote by $b_{w,t,a}$ denote the best solution by time $t$ of approach $a$ over instance $w$. Then, the mean relative error at time $t$ for approach $a$ on instance $w$ is given by $$MRE(w,t,a) = \frac{b_{w,t,a}}{b_w}.$$ We can now average over the different instances at time $t$. The average performance of approach $a$ at time $t$, $MRE(t,a)$ can be computed as $$MRE(t,a) = \frac{1}{|\mathcal{W}|}\sum_{ w\in\mathcal{W}} MRE(w,t,a).$$
We shall present this quantity ($MRE(t,a)$) for each of the approaches over time to demonstrate the speed of convergence of the proposed LS-based methods.

@@

In this part, we present the main findings of our empirical evaluation. 
We shall start by showing the best attained solutions by all methods.
Table~\ref{tab:results1} contains the best energy (in kW/hour) attained by the methods
for the 12 WFLO instances after $100$ seconds of runtime for the exact methods. The runtime for DA-LS was always less than $10$ seconds.
We observe that...

Table~\ref{tab:results2} shows the same type of results after $3600$ seconds.

\begin{table}[t]

@@

\begin{table}[t]

@@

\begin{figure}[t]%
